### 2020-05-18 Report/aws_325ghz_study.tex
Made a first version of the report's introduction section.

\section{Introduction}
%
\dots

@@

Two calculations were performed for each atmospheric cases. One ''clear-sky''
where all hydrometeors contents were set to zero, and one ``all-sky'' where IWC
and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were
included. Both sets of calculations were were made by ARTS's interface to the
RT4 solver \citep{evans1995microwavec}. This ``scattering solver'' was used
also for clear-sky, to avoid a possible bias between clear-sky and all-sky for
insignificant hydrometeor contents. RT4 handles the first two elements of the
Stokes vector, that were converted to brightness temperatures for H- and V-
polarisation.

@@

For water vapour the present settings in RTTOV are applied. That is, largely
MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
transitions are replaced \citep{saunders2018update,turner2019amsutran}.

@@

\begin{figure}[!tb]
  \centering
  \includegraphics[height=65mm]{fascod_wf_325l_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=65mm]{fascod_wf_325u_tro}
  \caption{RH weighting functions for the lower (left) and upper (right) side
    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
    bandwidth. The stated frequencies are the centre frequency of each. In
    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
    top-to-bottom in the order given in the legends). }
  \label{fig:wfuns:325ul}
\end{figure}

@@

@@

\begin{table}[!b]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000\\
    AWS-42  & 325.15$\pm$3.55 & 2500\\
    AWS-43  & 325.15$\pm$1.60 & 1200\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.60 & 2800\\
    AWS-42  & 325.15$\pm$4.05 & 1900\\
    AWS-43  & 325.15$\pm$2.35 & 1300\\
    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Preliminary specifications of AWS 325\,GHz channels, in the case of
    of three (left) and four (right) channels.}
  \label{tab:chs:prel}
\end{table}

\begin{figure}[!tb]
  \centering
  \includegraphics[height=64mm]{fascod_3chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=64mm]{fascod_3chopt_mlw}
  \caption{RH weighting functions of the three channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
    winter (right) scenarios.}
  \label{fig:3ch:prel}
\end{figure}
\begin{figure}[!tb]
  \centering
  \includegraphics[height=64mm]{fascod_4chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=64mm]{fascod_4chopt_mlw}
  \caption{RH weighting functions of the four channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
    winter (right) scenarios.}
  \label{fig:4ch:prel}
\end{figure}

>>>>

\section{Introduction}
%
\subsection{Background}
The Arctic Weather Satellite (AWS) is a small platform carrying a single
radiometer package. This instrument is an across-track scanning microwave
radiometer. The exact channel configuration of AWS is not yet set. The main
issue for this report is that AWS will have channels at 183\,GHz, but also one
or several channels a higher frequencies. A number of channels around 325\,GHz
was considered as the main option before AWS became an ESA/EUMETSAT mission,
but it has now also been suggested to have a single channel at 229\,GHz. This
suggestion is based on MWS (MicroWave Sounder), one of the instruments onboard
the next generation of Metop satellites. The 229\,GHz was added to MWS as an
help for performing cloud screening of 183\,GHz data
\citep{rekha2012potential}. For comparison, it can be mentioned that ICI (Ice
Cloud Imager), another new Metop sensor, will include 325\,GHz channels.

\subsection{Aim}
%
To support the selection between 229 and 325\,GHz channels for AWS, this report
investigates the possibility to use the later range in forming 183\,GHz data of
``clear-sky'' character. That is, following \citet{rekha2012potential}, the
assumption, is that the 183\,GHz data will be used in an system not yet
capable of doing ``all -sky'' assimilation.

In \citet{rekha2012potential} the task was defined to screen out observations
having a cloud impact exceeding 4\,K at 183$\pm$7\,GHz. Their final suggestion
for screening does not involve data from any other channel than 229\,GHz, but
requires radiative transfer calculations (as a ``B-O test'' is made). Only 
screening of 183$\pm$7\,GHz was discussed.

In this report, the task is defined in a somewhat different manner. The aim is
not just to estimate the cloud impact, but also to investigate to which degree
the cloud impact can be removed, i.e.\ to make a cloud correction. Further, in
this report only schemes that can be based directly on AWS data will be
considered and versions involving ``B-O tests'' are left for possible future
studies. On the other hand, cloud correction of all AWS 183\,GHz channels are
investigated. Another important difference is that our simulations aim to be a
random sample of real situations, while the simulations of
\citet{rekha2012potential} have a strong over-representation of cloudy
cases.

\subsection{Comparison to \citet{rekha2012potential}}
%
Results from \citet{rekha2012potential} will be used as reference. They did not
suggest specific settings of their algorithm. The main consideration of the
scheme is a threshold value. We assume below 6\,K for
this value, as it used most frequently as example in
\citet{rekha2012potential}. According to their Table~3, this results in that
2.4\% of the ``cloudy'' cases are miss-classified as ``clear''. We assume that
these cases have a cloud impact of 4 to 8\,K (i.e.\ the screening is 100\%
successful for cloud impact above 8\,K). For a 6\,K threshold 41\% of the
``clear'' cases are classified as ``cloudy'' and a removed in the screening
process.

The selected threshold value is towards the high side of the ones considered by 
\citet{rekha2012potential}. A lower value improves the removal of ``cloudy'' cases,
but the fraction of incorrectly removed ``clear'' cases increases quickly. For
example, a threshold of 3\,K decreases the miss-classification of ``cloudy''
cases to 0.6\%, but increases the miss-classification for ``clear'' cases to 77\%.
If 183$\pm$7\,GHz is classified as cloudy, we assume that also the data from
other 183\,GHz channels are rejected.

@@

Two calculations were performed for each atmospheric cases. One ''clear-sky''
where all hydrometeors contents were set to zero, and one ``all-sky'' where IWC
and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were
included. Both sets of calculations were were made by ARTS's interface to the
RT4 solver \citep{evans1995microwavec}. This ``scattering solver'' was used
also for clear-sky, to avoid a possible bias between clear-sky and all-sky for
insignificant hydrometeor contents. RT4 handles the first two elements of the
Stokes vector, that were converted to brightness temperatures for H- and
V-polarisation.

@@

For water vapour the present settings in RTTOV are applied. That is, largely
MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
transitions are replaced \citep{saunders2018update,turner2019amsutran}. A
smaller comparison to RTTOV has been made, that indciated an agreement better
than 0.1\,K in general. Deviations between 0.1 and 0.2\,K were found for some
channels at incidence angles above 40$^\circ$.

@@

@@

\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_wf_325l_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_wf_325u_tro}
  \caption{RH weighting functions for the lower (left) and upper (right) side
    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
    bandwidth. The stated frequencies are the centre frequency of each. In
    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
    top-to-bottom in the order given in the legends). }
  \label{fig:wfuns:325ul}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_3chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3chopt_mlw}
  \caption{RH weighting functions of the three channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
    winter (right) scenarios.}
  \label{fig:3ch:prel}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_4chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_4chopt_mlw}
  \caption{RH weighting functions of the four channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
    winter (right) scenarios.}
  \label{fig:4ch:prel}
\end{figure}

@@

\begin{table}[!t]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000\\
    AWS-42  & 325.15$\pm$3.55 & 2500\\
    AWS-43  & 325.15$\pm$1.60 & 1200\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.60 & 2800\\
    AWS-42  & 325.15$\pm$4.05 & 1900\\
    AWS-43  & 325.15$\pm$2.35 & 1300\\
    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Preliminary specifications of AWS 325\,GHz channels, in the case of
    of three (left) and four (right) channels.}
  \label{tab:chs:prel}
\end{table}
